Robustness of MinD oscillation in \emph{Escherichia coli} with diverse cell shapes

### 2014-11-05 paper/paper-MinD.tex
more work on making PNAS formatting beautiful and correct Tested everything on bennet.

\title{Robustness of MinD oscillation in \textbf{\emph{Escherichia coli}} with
  diverse cell shapes}

@@

@@

%% \begin{figure}
%%   \includegraphics[width=\columnwidth]{reactions}
%%   \caption{Reactions included in the model of Huang \emph{et
%%       al.}~\cite{huang2003dynamic}.}\label{fig:reactions}
%% \end{figure}

@@

@@

%% \begin{figure}
%%   \includegraphics[width=\columnwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/correlation.pdf}
%%   \caption{Temporal correlation function of the total MinD found in
%%     two opposite polar regions of the pill-shaped cell, shown against
%%     the correlation time.  Data for both the the determinisitic and
%%     stochastic models are shown.  The stochastic model shows an
%%     oscillation period of 39.5 seconds and coherence time of 307 seconds.
%%     The correlation functions are scaled to have the same initial
%%     value.}
%%   \label{corr-pill}
%% \end{figure}

@@

%% \begin{figure}
%%   \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-full_array/plots/correlation.pdf}
%%   \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-2_35-1_32-0_00-15_00-full_array/plots/correlation.pdf}
%%   \caption{Temporal correlation function of the total MinD found in
%%     two opposite polar regions of the shape \emph{A} (above) and the
%%     stadium \emph{A} (below) cell shapes, shown against the
%%     correlation time.  Data for both the the determinisitic and
%%     stochastic models are shown, and the correlation functions are
%%     scaled to have the same initial value.  For shape \emph{A}, the
%%     stochastic model shows an oscillation period of 53.1 seconds and
%%     coherence time of 246 seconds, so that it takes roughly 4.6 periods
%%     for the behavoir to decohere.  For the stadium \emph{A}, the same
%%     model shows an oscillation period of 51 seconds and coherence time of
%%     323 seconds, so that it takes roughly 6.3 periods for the behavoir
%%     to decohere.}
%%   \label{fig:corr-pancake-A}
%% \end{figure}

@@

%% \begin{figure}
%%   \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_60-28_60-94_00-15_00-full_array/plots/correlation.pdf}
%%   \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-2_92-1_18-0_00-15_00-full_array/plots/correlation.pdf}
%%   \caption{Correlation for B shapes}
%%   \label{corr-B}
%% \end{figure}

@@

\bibliographystyle{plain}
\bibliography{paper-one}
\end{article}

%\section*{Appendix}
\begin{acknowledgments}
This work was partially supported by
Spanish Ministry of Science and Technology Grant BFM2002-02042 (to D.C. and
J.L.R.) and by National Science Foundation Grand DMS-0245242 (to C.F.).
\end{acknowledgments}

\begin{figure}
  \includegraphics[width=\columnwidth]{reactions}
  \caption{Reactions included in the model of Huang \emph{et
      al.}~\cite{huang2003dynamic}.}\label{fig:reactions}
\end{figure}

\begin{figure*}
  %\includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/image-plot}
  \begin{center}
    \includegraphics[width=0.8\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/single-image-plot}\\
    \vspace{-1.5em}
    \includegraphics[width=0.8\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/single-image-plot}
    \vspace{-1.5em}
  \end{center}
  \caption{Images of the concentration of each protein species in a
    natural pill-shaped bacterium at one-second time intervals. The
    upper plots shows results from the deterministic model and the
    lower shows results from the stochastic model.  The order of
    frames is such that individual MinD proteins begin at the bottom
    of the plot (in the MinD:ATP state in the cytoplasm), and progress
    upward until they reach the MinE:MinD:ATP membrane-bound complex.
    At that point, they will spontaneously dissociate into cytoplasmic
    MinE (the top row) and the starting state of cytoplasmic
    MinD:ADP.}.
  \label{image-p}
\end{figure*}

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/correlation.pdf}
  \caption{Temporal correlation function of the total MinD found in
    two opposite polar regions of the pill-shaped cell, shown against
    the correlation time.  Data for both the the determinisitic and
    stochastic models are shown.  The stochastic model shows an
    oscillation period of 39.5 seconds and coherence time of 307 seconds.
    The correlation functions are scaled to have the same initial
    value.}
  \label{corr-pill}
\end{figure}

\begin{figure*}
  \centering
  \includegraphics[width=0.8\textwidth]{../paper/plot-ave}
  \caption{We display here arrows depicting successive maxima in space
    and and time overlayed on a color plot of the total MinD density
    averaged over the same time period.  The simulation time covered
    for the flattened cells is 350 seconds, which is the same
    period of time depicted in the experimental data plots of Mannik
    \emph{et al.}~\cite{mannik2012robustness}.  For the wild-type pill
    shape, we only cover 250 seconds, in order to provide a
    useful comparison due to its shorter oscillation period.  The top
    row shows plots published by Mannik of the MinD maxima behavoir
    and the bottom two rows show our simulations using the stochastic
    and deterministic models, respectively.  We simulated
    approximations to the two shapes observed by Mannik, which we call
    \emph{shape A} and \emph{shape B}.  In addition, we studied two
    flattened stadium shapes which we call \emph{stadium A} and
    \emph{stadium B} corresponding in aspect ratio and thickness to
    the two experimental shapes.  The spatial length scale of all the
    figures shown was identical. Each of the flattened cell shapes
    uses the same color scale for the number of proteins per unit
    area.  Finally, we display the natural pill shape, which was also
    featured in Figs.~\ref{image-p} and~\ref{corr-pill}, with a
    different color scale to reflect the thicker cell containing more
    proteins per cross-sectional area.  }
  \label{randst-plot-ave}
\end{figure*}

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-full_array/plots/correlation.pdf}
  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-2_35-1_32-0_00-15_00-full_array/plots/correlation.pdf}
  \caption{Temporal correlation function of the total MinD found in
    two opposite polar regions of the shape \emph{A} (above) and the
    stadium \emph{A} (below) cell shapes, shown against the
    correlation time.  Data for both the the determinisitic and
    stochastic models are shown, and the correlation functions are
    scaled to have the same initial value.  For shape \emph{A}, the
    stochastic model shows an oscillation period of 53.1 seconds and
    coherence time of 246 seconds, so that it takes roughly 4.6 periods
    for the behavoir to decohere.  For the stadium \emph{A}, the same
    model shows an oscillation period of 51 seconds and coherence time of
    323 seconds, so that it takes roughly 6.3 periods for the behavoir
    to decohere.}
  \label{fig:corr-pancake-A}
\end{figure}

>>>>

\title{Robustness of MinD oscillation in \emph{Escherichia coli} with
  diverse cell shapes}

@@

\significancetext{In order to determine blah de blah...}

@@

\begin{figure}
  \includegraphics[width=8.7cm]{reactions}
  \caption{Reactions included in the model of Huang \emph{et
      al.}~\cite{huang2003dynamic}.}\label{fig:reactions}
\end{figure}

@@

\begin{figure*}
  %\includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/image-plot}
  \begin{center}
    \includegraphics[height=6.4cm]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/single-image-plot}\\
    \vspace{-1.5em}
    \includegraphics[height=6.4cm]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/single-image-plot}
    \vspace{-1.5em}
  \end{center}
  \caption{Images of the concentration of each protein species in a
    natural pill-shaped bacterium at one-second time intervals. The
    upper plots shows results from the deterministic model and the
    lower shows results from the stochastic model.  The order of
    frames is such that individual MinD proteins begin at the bottom
    of the plot (in the MinD:ATP state in the cytoplasm), and progress
    upward until they reach the MinE:MinD:ATP membrane-bound complex.
    At that point, they will spontaneously dissociate into cytoplasmic
    MinE (the top row) and the starting state of cytoplasmic
    MinD:ADP.}.
  \label{image-p}
\end{figure*}

@@

\begin{figure}
  \begin{center}
    \includegraphics[height=6.4cm]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/correlation.pdf}
  \end{center}
  \caption{Temporal correlation function of the total MinD found in
    two opposite polar regions of the pill-shaped cell, shown against
    the correlation time.  Data for both the the determinisitic and
    stochastic models are shown.  The stochastic model shows an
    oscillation period of 39.5 seconds and coherence time of 307 seconds.
    The correlation functions are scaled to have the same initial
    value.}
  \label{corr-pill}
\end{figure}

@@

\begin{figure*}
  \centering
  \includegraphics[width=16cm]{../paper/plot-ave}
  \caption{We display here arrows depicting successive maxima in space
    and and time overlayed on a color plot of the total MinD density
    averaged over the same time period.  The simulation time covered
    for the flattened cells is 350 seconds, which is the same
    period of time depicted in the experimental data plots of Mannik
    \emph{et al.}~\cite{mannik2012robustness}.  For the wild-type pill
    shape, we only cover 250 seconds, in order to provide a
    useful comparison due to its shorter oscillation period.  The top
    row shows plots published by Mannik of the MinD maxima behavoir
    and the bottom two rows show our simulations using the stochastic
    and deterministic models, respectively.  We simulated
    approximations to the two shapes observed by Mannik, which we call
    \emph{shape A} and \emph{shape B}.  In addition, we studied two
    flattened stadium shapes which we call \emph{stadium A} and
    \emph{stadium B} corresponding in aspect ratio and thickness to
    the two experimental shapes.  The spatial length scale of all the
    figures shown was identical. Each of the flattened cell shapes
    uses the same color scale for the number of proteins per unit
    area.  Finally, we display the natural pill shape, which was also
    featured in Figs.~\ref{image-p} and~\ref{corr-pill}, with a
    different color scale to reflect the thicker cell containing more
    proteins per cross-sectional area.  }
  \label{randst-plot-ave}
\end{figure*}

\begin{figure}
  \begin{center}
    \includegraphics[height=6.4cm]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-full_array/plots/correlation.pdf}\\
    \includegraphics[height=6.4cm]{../data/shape-stad/0_25-2_35-1_32-0_00-15_00-full_array/plots/correlation.pdf}
  \end{center}
  \caption{Temporal correlation function of the total MinD found in
    two opposite polar regions of the shape \emph{A} (above) and the
    stadium \emph{A} (below) cell shapes, shown against the
    correlation time.  Data for both the the determinisitic and
    stochastic models are shown, and the correlation functions are
    scaled to have the same initial value.  For shape \emph{A}, the
    stochastic model shows an oscillation period of 53.1 seconds and
    coherence time of 246 seconds, so that it takes roughly 4.6 periods
    for the behavoir to decohere.  For the stadium \emph{A}, the same
    model shows an oscillation period of 51 seconds and coherence time of
    323 seconds, so that it takes roughly 6.3 periods for the behavoir
    to decohere.}
  \label{fig:corr-pancake-A}
\end{figure}

@@

%% \begin{figure}
%%   \includegraphics[width=8.7cm]{../data/shape-randst/0_25-18_60-28_60-94_00-15_00-full_array/plots/correlation.pdf}
%%   \includegraphics[width=8.7cm]{../data/shape-stad/0_25-2_92-1_18-0_00-15_00-full_array/plots/correlation.pdf}
%%   \caption{Correlation for B shapes}
%%   \label{corr-B}
%% \end{figure}

@@

%% %\section*{Appendix}
%% \begin{acknowledgments}
%% This work was partially supported by
%% Spanish Ministry of Science and Technology Grant BFM2002-02042 (to D.C. and
%% J.L.R.) and by National Science Foundation Grand DMS-0245242 (to C.F.).
%% \end{acknowledgments}

\bibliographystyle{plain}
\bibliography{paper-MinD}
\end{article}

%% \clearpage

%% \begin{figure}
%%   \includegraphics[width=8.7cm]{reactions}
%%   \caption{Reactions included in the model of Huang \emph{et
%%       al.}~\cite{huang2003dynamic}.}\label{fig:reactions}
%% \end{figure}

%% \begin{figure}
%%   \includegraphics[width=8.7cm]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/correlation.pdf}
%%   \caption{Temporal correlation function of the total MinD found in
%%     two opposite polar regions of the pill-shaped cell, shown against
%%     the correlation time.  Data for both the the determinisitic and
%%     stochastic models are shown.  The stochastic model shows an
%%     oscillation period of 39.5 seconds and coherence time of 307 seconds.
%%     The correlation functions are scaled to have the same initial
%%     value.}
%%   \label{corr-pill}
%% \end{figure}

%% \begin{figure}
%%   \includegraphics[width=8.7cm]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-full_array/plots/correlation.pdf}
%%   \includegraphics[width=8.7cm]{../data/shape-stad/0_25-2_35-1_32-0_00-15_00-full_array/plots/correlation.pdf}
%%   \caption{Temporal correlation function of the total MinD found in
%%     two opposite polar regions of the shape \emph{A} (above) and the
%%     stadium \emph{A} (below) cell shapes, shown against the
%%     correlation time.  Data for both the the determinisitic and
%%     stochastic models are shown, and the correlation functions are
%%     scaled to have the same initial value.  For shape \emph{A}, the
%%     stochastic model shows an oscillation period of 53.1 seconds and
%%     coherence time of 246 seconds, so that it takes roughly 4.6 periods
%%     for the behavoir to decohere.  For the stadium \emph{A}, the same
%%     model shows an oscillation period of 51 seconds and coherence time of
%%     323 seconds, so that it takes roughly 6.3 periods for the behavoir
%%     to decohere.}
%%   \label{fig:corr-pancake-A}
%% \end{figure}
